---
title: "DataVisualization(Sprint5-HW)"
author: "Note B"
date: "2023-02-25"
output:
  pdf_document: default
  html_document: default
---

***
<h2 style="color:blue" align="center"> Sprint5 Data Visualization Homework </h2>
***

### **Question** Explore dataframe *'diamonds'* and create 5 visualizations

R library loading
```{r message=FALSE, warning=FALSE}
library (tidyverse)
library (ggplot2)
library (patchwork)
library (dplyr)
library (scales)
```

<h4 style="color:blue"> Hw1# Summary count by cut types with accending order </h4>
```{r}
ggplot(diamonds, aes(x = fct_infreq(cut))) +
  geom_bar(stat = "count", fill = "#287860", col = "black") +
  stat_count(geom = "text", color ="white", size=3.5,
             aes(label = after_stat(count)), position=position_stack(vjust=0.5)) +
  theme_minimal() +
  labs (
    title = "Diamond qantity group by cut type",
    x = "Cut Types",
    y = "Quantity (ea.)",
    caption = "Datasource: diamonds ggplot2"
  )
```

##### ***HW#1 Conclusion:*** *The most quantity of diamond cut types is 'Ideal' with 21,551 ea and the least is 'Fair' with 1,610 ea.*

***

<h4 style="color:blue"> Hw2# Pie chart by clarity </h4>
```{r}
t1 <- diamonds %>%
  group_by(clarity) %>%
  count() %>%
  ungroup() %>%
  mutate(perc = n/sum(n)) %>%
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(t1, aes(x="", y=perc, fill=clarity)) +
  geom_col()+
  geom_text (aes (label=labels),
             position = position_stack(vjust=0.5))+
  coord_polar(theta = "y")+
  theme_void()+
  scale_fill_brewer(type="qual", palette = 4) +
  labs (
    title = "% of diamonds by clarity",
    caption = "Datasource: diamonds ggplot2"
  )
```

##### ***HW#2 Conclusion:*** *Total of eight(8) diamond clarity, top 3 of clarity are 1) 24.2% SI1, 22.7% VS2, and 17% SI2.*

***

<h4 style="color:blue"> Hw3# Boxplot of caret by color </h4>
```{r}
set.seed(07)
ggplot(diamonds %>% sample_n(5000), aes (x=color, y=carat, fill=color)) +
  geom_boxplot(alpha=0.3) +
  theme(legend.position="none") +
  scale_fill_brewer(type="seq", palette = 6) +
  theme_minimal() +
  labs (
    title = "Boxplot of diamonds caret by color",
    caption = "Datasource: diamonds ggplot2"
  )
```

##### ***HW#3 Conclusion:*** *Increasing trend of carat following to color (D>E>F>G>H>I>J)*

***

<h4 style="color:blue"> Hw4# Scatter plot between price and caret </h4>
```{r}
set.seed(07)
ggplot(diamonds %>% sample_n(1000), aes (x=carat, y=price)) +
  geom_point(size=4, alpha=0.2, col="#883399") +
  geom_smooth(method="auto", col="#7F6FAF") +
  theme_minimal() +
  labs (
    title = "Relationship between price and caret of diamonds",
    caption = "Datasource: diamonds ggplot2"
  )
```

##### ***HW#4 Conclusion:*** *There is relationship between price and carat. Price is higher follow to carat value*

***

<h4 style="color:blue"> Hw5# using facet </h4>
```{r}
set.seed(07)
  ggplot(diamonds %>% sample_n(1000), mapping =aes(x=carat, y=price, col=color)) +
    geom_point(size=4, alpha=0.2) +
    scale_fill_brewer(type="qual", palette = 6) +
    facet_wrap(~clarity) +
    theme_minimal() +
    labs (
      title = "Relationship between price and caret of diamonds, separate by clarity",
      caption = "Datasource: diamonds ggplot2"
    )
```

##### ***HW#5 Conclusion:*** *Price is depended on carat value for all colors*

***

