---
title: "Homework Data Viz"
author: "Note B"
date: "2023-02-25"
output: html_document
---

# Hello World

This is markdown language. Today we learn a few topics in R.

-   databases
-   working with date
-   ggplot2
-   rmarkdown

## header2 haha

### header3 R programming

#### h4

## Homework

Explore dataframe 'diamonds' and create 5 visualization

### Chart 1 - releationshipt between carat and price

```{r message=FALSE, warning=FALSE}
library (tidyverse)
head (diamonds)
```

My first chart

```{r}
set.seed(42)
ggplot (diamonds %>% sample_n(500),
        aes (carat, price))+
  geom_point()+
  geom_smooth()
```

We found a positive relationship between two variables.

Another chart

```{r}
ggplot (diamonds, mapping = aes(cut, fill=color)) +
  geom_bar(position = "fill") +
  theme_minimal()
```

comment what did we find in this charts?

[google](https://www.google.com)

[datarockie](https://datarockies.com)

Add an image to this report.

![new image](https://images.unsplash.com/photo-1518770660439-4636190af475?ixlib=rb-4.0.3&ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&auto=format&fit=crop&w=1740&q=80)
